Software Citation Principles

### 2016-07-26 sc-principles/software-citation-principles.tex
all of the outputs -> all outputs

As the process of research\footnote{We use the term ``research'' in this document to include work intended to increase human knowledge and benefit society, in science, engineering, humanities, and other areas.} has become increasingly digital, research outputs
and products have grown beyond simply papers and books to include software,
data, and other electronic components such as presentation slides, posters,
(interactive) graphs, maps, websites (e.g., blogs and forums), and multimedia
(e.g., audio and  video lectures).  Research knowledge is embedded in these
components. And papers and books themselves are also becoming increasingly
digital, allowing them to become executable and reproducible. As we move towards
this future where research is performed in and recorded as a variety of linked
digital products, the characteristics and properties that developed for books
and papers need to be applied to all digital products and possibly adjusted.
Here, we are concerned specifically with the citation of software products. The
challenge is not just the textual citation of software in a paper, but the more
general identification of software used within the research process. This work is
focused on making software a citable entity throught the scholarly ecosystem. While
software products are a relatively small fraction of the sum total of
research output, this work together with other efforts such as the Force11
Data Citation Principles~\cite{data-citation-principles} collectively represent
an effort to better describe all of the outputs of research.

>>>>

As the process of research\footnote{We use the term ``research'' in this document to include work intended to increase human knowledge and benefit society, in science, engineering, humanities, and other areas.} has become increasingly digital, research outputs
and products have grown beyond simply papers and books to include software,
data, and other electronic components such as presentation slides, posters,
(interactive) graphs, maps, websites (e.g., blogs and forums), and multimedia
(e.g., audio and  video lectures).  Research knowledge is embedded in these
components. And papers and books themselves are also becoming increasingly
digital, allowing them to become executable and reproducible. As we move towards
this future where research is performed in and recorded as a variety of linked
digital products, the characteristics and properties that developed for books
and papers need to be applied to all digital products and possibly adjusted.
Here, we are concerned specifically with the citation of software products. The
challenge is not just the textual citation of software in a paper, but the more
general identification of software used within the research process. This work is
focused on making software a citable entity throught the scholarly ecosystem. While
software products are a relatively small fraction of the sum total of
research output, this work together with other efforts such as the Force11
Data Citation Principles~\cite{data-citation-principles} collectively represent
an effort to better describe all outputs of research.
